%------------------------
% Resume Template
% Author : Anubhav Singh
% Github : https://github.com/xprilion
% License : MIT
%------------------------

\documentclass[a4paper,20pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{#3} & \textit{#4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-3pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-----------------------------
%%%%%%  CV STARTS HERE  %%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\LARGE Abhishek Tentiwala}} & Email: \href{mailto:atentiwala@gmail.com}{atentiwala@gmail.com}\\
  \href{https://www.linkedin.com/in/abhishek-tentiwala-5bb781335?utm_source=share&utm_campaign=share_via&utm_content=profile&utm_medium=android_app}{LinkedIn: Abhishek Tentiwala} & Mobile:~~~+91-7668339061 \\
  \href{https://github.com/AbhishekTentiwala}{GitHub: ~~github.com/AbhishekTentiwala} \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{~~Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {National Institute of Technology Agartala}{Tripura, India}
    {Bachelor of Technology - Computer Science and Technology; GPA: 9.22}{2024 - 2028}
    {\scriptsize \textit{\footnotesize{\newline{}\textbf{JEE Mains:} (Year 2024) Percentile - 98.89}}}
    {\scriptsize \textit{\footnotesize{\newline{}\textbf{JEE Advanced:} (Year 2024) AIR - 22700}}}
    {\scriptsize \textit{\footnotesize{\newline{}\textbf{Intermediate:} Dhanuka Senior Sec. School, Mathura (Year 2023) Percentage - 93}}}
    {\scriptsize \textit{\footnotesize{\newline{}\textbf{Matriculation:} Dhanuka Senior Sec. School, Mathura (Year 2021) Percentage - 97.4}}}
\resumeSubHeadingListEnd

\vspace{-5pt}
\section{Skills Summary}
\resumeSubHeadingListStart
  \resumeSubItem{Languages}{~~~~~~Python, C++, TypeScript, JavaScript, SQL, Bash}
  \resumeSubItem{Frameworks}{~~~~React, Next.js, Node.js, Express.js}
  \resumeSubItem{Tools}{~~~~~~~~~~~~~~Git, PostgreSQL, MySQL, SQLite}
  \resumeSubItem{Soft Skills}{~~~~~~~Leadership, Event Management, Writing, Public Speaking, Time Management}
\resumeSubHeadingListEnd

\vspace{-5pt}
\section{Coding Platforms}
\begin{description}[font=$\bullet$]
\item {1000+ contest rating on Codeforces.}
\vspace{-5pt}
\item {Solved 500+ problems across platforms: \href{https://codeforces.com/profile/AbhishekTentiwala}{Codeforces}, \href{https://leetcode.com/u/abt09}{LeetCode}, CodeChef, and \href{https://www.geeksforgeeks.org/profile/atentijcp0}{GeeksforGeeks}.}
\end{description}

%-----------PROJECTS-----------------
\vspace{-5pt}
\section{Projects and Contributions}
\resumeSubHeadingListStart

\resumeSubItem{Chatter - Web application for messaging and file sharing \href{https://github.com/AbhishekTentiwala/Chater}{(GitHub)} (Next.js, Prisma, PostgreSQL, UploadThing third-party service for file sharing, WebSockets)}
{(Work in Progress) A self-paced personal project to learn different tech stacks with admin access implementation and chat room concepts. (Summer 2025)}

\vspace{2pt}
\resumeSubItem{RecyCool - Buy and Sell website for NIT Agartala by E-Cell \href{https://github.com/ecellnita/Campus_Recycle}{(GitHub)} (Next.js, MongoDB, Express.js, Cloudinary, Nodemailer)}
{(Work in Progress) Contributed as both front-end and back-end developer as a core tech team member of E-Cell NITA to resolve issues and improve project practicality.}

\vspace{2pt}
\resumeSubItem{Mokshya - College fest website \href{https://github.com/AbhishekTentiwala/mokshya_new}{(GitHub)} (Next.js, MongoDB, Express.js, Tailwind CSS)}
{Led a team of three members to develop the website for the college cultural fest under three days, gaining experience working under pressure. (Dec 2025)}

\resumeSubHeadingListEnd

\vspace{-5pt}
\section{Position of Responsibility}
\begin{description}[font=$\bullet$]
\item {Core Member, E-Cell, NIT-A: Contributed to the development and maintenance of technical projects for the Entrepreneurship Cell. Actively participated in initiatives, event organization, and technical support.}
\item {Core Member, WeCan, NIT-A: Contributed to the development and maintenance of a mobile application for data management and other technical support.}
\end{description}

\vspace{-5pt}
\section{Extracurricular}
\begin{description}[font=$\bullet$]
\item {Hosted and anchored the E-Cell club event Initiate 4.0, showcasing strong public speaking, event coordination, and audience engagement skills. (2023)}
\vspace{-5pt}
\item {Managed a collaboration event between WeCan and Malhar clubs of NIT Agartala.}
\end{description}

\end{document}
